Teaching

### 2025-11-18 books/index.qmd
fixed book image link, added welcome info, and added 214 to teaching page

<img src="images/veridical-data-science-cover.jpg" alt="Veridical Data Science Book Cover" style="float:left; margin:0 2em 1em 0; width:200px; border-radius:8px;" />

>>>>

<img src="../images/veridical-data-science-cover.jpg" alt="Veridical Data Science Book Cover" style="float:left; margin:0 2em 1em 0; width:200px; border-radius:8px;" />

### 2025-11-18 index.qmd
Add spaces to impose newlines.
fixed book image link, added welcome info, and added 214 to teaching page

Address: 367 Evans Hall #3860, Berkeley, CA 94720  
Phone: 510-642-2781  
Fax: 510-642-7892  
Email: [binyu@berkeley.edu](mailto:binyu@berkeley.edu)
:::

@@

>>>>

Address: 367 Evans Hall #3860, Berkeley, CA 94720  
Phone: 510-642-2781  
Fax: 510-642-7892  
Email: [binyu@berkeley.edu](mailto:binyu@berkeley.edu)

:::

@@

## Welcome

Professor Bin Yu is the head of the Yu Group at Berkeley, which consists of
12-15 students and postdocs from Statistics and EECS. She was formally trained
as a statistician, but her research interests and achievements extend beyond
the realm of statistics. Together with her group,  Bin Yu has leveraged new
computational developments to solve important scientific problems by combining
novel and often interpretable statistical machine learning approaches with the
domain expertise of my many collaborators in neuroscience, genomics and
precision medicine. She also develops relevant theory to understand random
forests and deep learning for insight into and guidance for practice.  Her work
has been recongized by many awards. In particular, she was inducted to the
National Academy of Sciences in 2014 and to the American Academy of Arts and
Sciences in 2013. She delivered the IMS Wald Lectures and COPSS Distinguished
Achievement and Award Lecture (DAAL, formerly Fisher Award and Lecture) in 2023.

She and her team have developed the PCS framework for veridical data science (or
responsible, reliable, and transparent data analysis and decision-making). PCS
stands for predictability, computability and stability, and it unifies,
streamlines, and expands on ideas and best practices of machine learning and
statistics.

In order to augment empirical evidence for decision-making, they are
investigating statistical machine learning methods/algorithms (and associated
statistical inference problems) such as dictionary learning, non-negative matrix
factorization (NMF), EM and deep learning (CNNs and LSTMs), and heterogeneous
effect estimation in randomized experiments (X-learner). Their recent algorithms
include staNMF for unsupervised learning, iterative Random Forests (iRF) and
signed iRF (s-iRF) for discovering predictive and stable high-order interactions
in supervised learning, next generation tree-based methods (e.g. fast and
interpretable greedy-tree sums (FIGS) and hierarchical shrinked (HS) trees, and
RF+), contextual decomposition (CD), aggregated contextual decomposition (ACD),
and adaptive wavelet distillation (AWD) for interpretation of Deep Neural
Networks (DNNs).

### 2025-11-18 teaching/index.qmd
fixed book image link, added welcome info, and added 214 to teaching page

@@

## STAT 215A - Statistical Models: Theory and Application

**Course Website:** [[STAT 215A](https://classes.berkeley.edu/content/2019-Fall-STAT-215A-001-LEC-001)]

>>>>

## STAT 215A - Applied Statistics and Machine Learning

**Course Website:** [[STAT 215A](https://classes.berkeley.edu/content/2025-fall-stat-215a-001-lec-001)]

## STAT 214 - Data Analysis and Machine Learning for Real-World Decision Making

**Course Description:** Students will be engaged in open-ended data projects for decision making to solve domain problems. It mirrors the entire data science life cycle in practice, including problem formulation, data cleaning, exploratory data analysis, statistical and machine learning modeling and computational techniques, and interpretation of results in context. It is guided by the Predictability-Computability-Stability (PCS) framework for veridical data science and emphasizes critical thinking and documenting human judgment calls and code. It coaches not only the technical but also communication and teamwork skills in order to obtain responsible and reliable data-driven conclusions for solving complex real world problems.

**Prerequisites:** Linear algebra, calculus, upper division probability and statistics, and familiarity with high-level programming languages.

**Course Website:** [[STAT 214](https://classes.berkeley.edu/content/2026-spring-stat-214-001-lec-001)]

@@
